---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

  [![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
  
*This is highly expermantal*
  

# parsesum

parsesum provides tools to analyze source code. To this end, it leverages
the R base parser.

## Example

For example, did you want to know how many functions you declared in your 
R package? Here is how you can get the names of all your named delared 
functions, enriched with some useful information, for example how many 
line each function declaration spans.
```{r}
library(parsesum)
fun_decs <- ls_fun_decs(".")
fun_decs
```

Wanna know which file contains most delcarations?
```{r}
library(dplyr)
fun_decs %>%
  group_by(.data$source) %>%
  count() %>%
  arrange(desc(n))
```

Or list according to longest name?
```{r}
fun_decs %>%
  mutate(nchar = nchar(.data$text)) %>%
  arrange(desc(.data$nchar))
```

Or wanna see the function that is the shortest in terms of lines used?
```{r}
fun_decs %>%
  arrange(.data$n_lines)
```

